### 2018-02-15 submission/manuscript.Rmd
update sig OR for unmatched tissue

***Mouth-Associated Genera are Associated with an Increased OR of Tumor:***
Next, we asked if being higher than the median relative abundance, for any specific genera, resulted in an altered OR for adenoma or carcinoma, in stool and colon tissue, due to our previous observations of small increases in OR using OTU richness and Shannon diversity. To investigate this we analyzed all common genera across each study, in colon tissue or stool, and assessed whether a relative abundance higher than the median results in an increase or decrease in OR. For both tissue and stool samples only ORs associated with an increase or decrease in carcioma tumors were significant after multiple comparison correction [Table S3 & S4]. Out of the `r length(crc_OR_stool$measure)` taxa that had significant ORs in stool samples `r length(filter(crc_OR_stool, measure %in% c("Fusobacterium", "Parvimonas", "Porphyromonas", "Peptostreptococcus"))[, "measure"])` were mouth-associated microbes. These mouth-associated genera significantly increased the ORs of carcinoma for stool samples and included *Fusobacterium*, *Parvimonas*, *Porphyromonas*, and *Peptostreptococcus* [Table S3]. Conversely, mouth-associated genera were not significantly associated with an increased OR for carcinoma in tissue samples [Table S4]. Only unmatched tissue samples had significant OR taxa and these were *Dorea* (OR = `r round(filter(crc_unmatched_OR_tissue, measure == "Dorea")[, "rr"], digits = 2)` (`r round(filter(crc_unmatched_OR_tissue, measure == "Dorea")[, "ci_lb"], digits = 2)` - `r round(filter(crc_unmatched_OR_tissue, measure == "Dorea")[, "ci_ub"], digits = 2)`)) and *Weissella* (OR = `r round(filter(crc_unmatched_OR_tissue, measure == "Weissella")[, "rr"], digits = 2)` (`r round(filter(crc_unmatched_OR_tissue, measure == "Weissella")[, "ci_lb"], digits = 2)` - `r round(filter(crc_unmatched_OR_tissue, measure == "Weissella")[, "ci_ub"], digits = 2)`)). Overall, there was little direct overlap in increased or decreased OR genera between both tumor type and sample site.

>>>>

***Mouth-Associated Genera are Associated with an Increased OR of Tumor:***
Next, we asked if being higher than the median relative abundance, for any specific genera, resulted in an altered OR for adenoma or carcinoma, in stool and colon tissue, due to our previous observations of small increases in OR using OTU richness and Shannon diversity. To investigate this we analyzed all common genera across each study, in colon tissue or stool, and assessed whether a relative abundance higher than the median results in an increase or decrease in OR. For both tissue and stool samples only ORs associated with an increase or decrease in carcioma tumors were significant after multiple comparison correction [Table S3 & S4]. Out of the `r length(crc_OR_stool$measure)` taxa that had significant ORs in stool samples `r length(filter(crc_OR_stool, measure %in% c("Fusobacterium", "Parvimonas", "Porphyromonas", "Peptostreptococcus"))[, "measure"])` were mouth-associated microbes. These mouth-associated genera significantly increased the ORs of carcinoma for stool samples and included *Fusobacterium*, *Parvimonas*, *Porphyromonas*, and *Peptostreptococcus* [Table S3]. Conversely, mouth-associated genera were not significantly associated with an increased OR for carcinoma in tissue samples [Table S4]. Only unmatched tissue samples had significant OR taxa and these were *Dorea* (OR = `r round(filter(crc_unmatched_OR_tissue, measure == "Dorea")[, "rr"], digits = 2)` (`r round(filter(crc_unmatched_OR_tissue, measure == "Dorea")[, "ci_lb"], digits = 2)` - `r round(filter(crc_unmatched_OR_tissue, measure == "Dorea")[, "ci_ub"], digits = 2)`)), *Blautia* (OR = `r round(filter(crc_unmatched_OR_tissue, measure == "Blautia")[, "rr"], digits = 2)` (`r round(filter(crc_unmatched_OR_tissue, measure == "Blautia")[, "ci_lb"], digits = 2)` - `r round(filter(crc_unmatched_OR_tissue, measure == "Blautia")[, "ci_ub"], digits = 2)`)), and *Weissella* (OR = `r round(filter(crc_unmatched_OR_tissue, measure == "Weissella")[, "rr"], digits = 2)` (`r round(filter(crc_unmatched_OR_tissue, measure == "Weissella")[, "ci_lb"], digits = 2)` - `r round(filter(crc_unmatched_OR_tissue, measure == "Weissella")[, "ci_ub"], digits = 2)`)). Overall, there was little direct overlap in increased or decreased OR taxa between both tumor type and sample site.

### 2018-02-15 submission/manuscript.tex
update sig OR for unmatched tissue

\textbf{\emph{Mouth-Associated Genera are Associated with an Increased
OR of Tumor:}} Next, we asked if being higher than the median relative
abundance, for any specific genera, resulted in an altered OR for
adenoma or carcinoma, in stool and colon tissue, due to our previous
observations of small increases in OR using OTU richness and Shannon
diversity. To investigate this we analyzed all common genera across each
study, in colon tissue or stool, and assessed whether a relative
abundance higher than the median results in an increase or decrease in
OR. For both tissue and stool samples only ORs associated with an
increase or decrease in carcioma tumors were significant after multiple
comparison correction {[}Table S3 \& S4{]}. Out of the 8 taxa that had
significant ORs in stool samples 4 were mouth-associated microbes. These
mouth-associated genera significantly increased the ORs of carcinoma for
stool samples and included \emph{Fusobacterium}, \emph{Parvimonas},
\emph{Porphyromonas}, and \emph{Peptostreptococcus} {[}Table S3{]}.
Conversely, mouth-associated genera were not significantly associated
with an increased OR for carcinoma in tissue samples {[}Table S4{]}.
Only unmatched tissue samples had significant OR taxa and these were
\emph{Dorea} (OR = 0.35 (0.22 - 0.55)) and \emph{Weissella} (OR = 5.15
(2.02 - 13.14)). Overall, there was little direct overlap in increased
or decreased OR genera between both tumor type and sample site.

>>>>

\textbf{\emph{Mouth-Associated Genera are Associated with an Increased
OR of Tumor:}} Next, we asked if being higher than the median relative
abundance, for any specific genera, resulted in an altered OR for
adenoma or carcinoma, in stool and colon tissue, due to our previous
observations of small increases in OR using OTU richness and Shannon
diversity. To investigate this we analyzed all common genera across each
study, in colon tissue or stool, and assessed whether a relative
abundance higher than the median results in an increase or decrease in
OR. For both tissue and stool samples only ORs associated with an
increase or decrease in carcioma tumors were significant after multiple
comparison correction {[}Table S3 \& S4{]}. Out of the 8 taxa that had
significant ORs in stool samples 4 were mouth-associated microbes. These
mouth-associated genera significantly increased the ORs of carcinoma for
stool samples and included \emph{Fusobacterium}, \emph{Parvimonas},
\emph{Porphyromonas}, and \emph{Peptostreptococcus} {[}Table S3{]}.
Conversely, mouth-associated genera were not significantly associated
with an increased OR for carcinoma in tissue samples {[}Table S4{]}.
Only unmatched tissue samples had significant OR taxa and these were
\emph{Dorea} (OR = 0.35 (0.22 - 0.55)), \emph{Blautia} (OR = 0.47 (0.3 -
0.73)), and \emph{Weissella} (OR = 5.15 (2.02 - 13.14)). Overall, there
was little direct overlap in increased or decreased OR taxa between both
tumor type and sample site.
